---
title: "3-1 Intro to Linear Regression"
output: html_document
---

# 3.6 Lab Section

```{r setup, include=FALSE}
library(MASS)
library(ISLR)
```

```{r}
lm.fit <- lm(medv~lstat, data = Boston)

# Or alternatively: 
# attach(Boston)
# lm.fit <- lm(medv~lstat)

lm.fit
summary(lm.fit) # More detailed information
names(lm.fit)

coef(lm.fit)
confint(lm.fit)

#The predict() function can be used to produce confidence intervals and prediction intervals for the prediction of medv using a given value of lstat

predict(lm.fit, data.frame(lstat = c(5, 10, 15)), interval = "confidence")
predict(lm.fit, data.frame(lstat = c(5, 10, 15)), interval = "prediction")

#Prediction interval has to predict the next data point, which may vary widely
#Confidence interval has to try to fit the mean of the data, which is more constrained

```

```{r}
attach(Boston)
plot(lstat, medv)
abline(lm.fit)

# Other fun plotting options 
abline (lm.fit ,lwd =3)
abline (lm.fit ,lwd =3, col ="red ")
plot(lstat ,medv ,col ="red ")
plot(lstat ,medv ,pch =20)
plot(lstat ,medv ,pch ="+")
plot (1:20 ,1:20, pch =1:20)


```
We can achieve this by using the par() function, which tells R to split the
display screen into separate panels so that multiple plots can be viewed simultaneously.
For example, par(mfrow=c(2,2)) divides the plotting region into a 2 × 2 grid of panels.

```{r}
par(mfrow = c(2,2))
plot(lm.fit)
```

Alternatively, we can compute the residuals from a linear regression fit using the residuals() function. The function rstudent() will return the studentized residuals, and we can use this function to plot the residuals against the fitted values. 

```{r}
plot(predict(lm.fit), residuals(lm.fit))
plot(predict(lm.fit), rstudent(lm.fit))
```

The residual plots suggest there may be some non-linearity. Leverage statistics can computed for any number of predictors using the hatvalues() function. 

```{r}
plot(hatvalues(lm.fit))
which.max(hatvalues(lm.fit))
```

The which.max() function identifies the index of the largest elementof a vector. In this case, it tells us which observation has the largest leverage statistic. 

# Problems 

8. This question involves the use of simple linear regression on the Auto data set.
(a) Use the lm() function to perform a simple linear regression with mpg as the response and horsepower as the predictor. Use the summary() function to print the results. Comment on the output.

```{r}
attach(Auto)
lm.fit <- lm(mpg~horsepower)
summary(lm.fit)
```

i. Is there a relationship between the predictor and the response?  
  Yes - Look at the low p-value for horsepower  
ii. How strong is the relationship between the predictor and the response?
  Low p-value, high t-value
iii. Is the relationship between the predictor and the response positive or negative?  
  It is negative, since the estimate is -0.1  
iv. What is the predicted mpg associated with a horsepower of 98? What are the associated 95% confidence and prediction intervals?  
```{r}
predict(lm.fit, data.frame(horsepower = 98), interval = "confidence")
predict(lm.fit, data.frame(horsepower = 98), interval = "prediction")
```
  

(b) Plot the response and the predictor. Use the abline() function to display the least squares regression line.

```{r}
plot(mpg, horsepower)
abline(lm.fit$coef, col = "red") #Something is wrong with this
```


(c) Use the plot() function to produce diagnostic plots of the least squares regression fit. Comment on any problems you see with the fit.

```{r}
par(mfrow = c(2,2))
plot(lm.fit)
```


13. In this exercise you will create some simulated data and will fit simple
linear regression models to it. 
```{r}
set.seed(1)
```

(a) Using the rnorm() function, create a vector, x, containing 100
observations drawn from a N(0, 1) distribution. This represents
a feature, X.

```{r}
x <- rnorm(100)
```


(b) Using the rnorm() function, create a vector, eps, containing 100
observations drawn from a N(0, 0.25) distribution i.e. a normal
distribution with mean zero and variance 0.25.

```{r}
eps <- rnorm(100, sd = sqrt(0.25))
```


(c) Using x and eps, generate a vector y according to the model
Y = −1 + 0.5X + E

```{r}
y <- -1 + 0.5 * x + eps
```


What is the length of the vector y? What are the values of β0
and β1 in this linear model?


(d) Create a scatterplot displaying the relationship between x and
y. Comment on what you observe.

```{r}

```


(e) Fit a least squares linear model to predict y using x. Comment
on the model obtained. How do ˆ β0 and ˆ β1 compare to β0 and
β1?
(f) Display the least squares line on the scatterplot obtained in (d).
Draw the population regression line on the plot, in a different
color. Use the legend() command to create an appropriate legend.
(g) Now fit a polynomial regression model that predicts y using x
and x2. Is there evidence that the quadratic term improves the
model fit? Explain your answer.
(h) Repeat (a)–(f) after modifying the data generation process in
such a way that there is less noise in the data. The model (3.39)
should remain the same. You can do this by decreasing the variance
of the normal distribution used to generate the error term
 in (b). Describe your results.
(i) Repeat (a)–(f) after modifying the data generation process in
such a way that there is more noise in the data. The model
(3.39) should remain the same. You can do this by increasing
the variance of the normal distribution used to generate the
error term  in (b). Describe your results.
(j) What are the confidence intervals for β0 and β1 based on the
original data set, the noisier data set, and the less noisy data
set? Comment on your results.

15. This problem involves the Boston data set, which we saw in the lab
for this chapter. We will now try to predict per capita crime rate
using the other variables in this data set. In other words, per capita
crime rate is the response, and the other variables are the predictors.
(a) For each predictor, fit a simple linear regression model to predict
the response. Describe your results. In which of the models is
there a statistically significant association between the predictor
and the response? Create some plots to back up your assertions.

